---
title: "lab-2"
author: "manohar"
date: "September 9, 2017"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1)a)What is the result of the following code?

```{r}
nth <- paste(1:12, c("st", "nd", "rd", rep("th", 9)), sep = "")
paste(month.abb, nth, sep = " ")
paste(month.abb, nth, sep = " ", collapse = "; ")
```

##b) Explain in your own words the difference between the last two paste() calls above. What does collapse do?

--The first paste function brings in two vectors month.abb with months and nth which we created and produces a 12 invidual strings whereas while using collapse argument concatenates into a single string .

##c) What do you expect the following code to do?
concatenates all months in month.abb with ; into a single string with collapse
```{r}
paste(month.abb, collapse = "; ")
```

##d)Below are the keys (variable keys) and values (variable values). Write code to create a string JSON
object denoting the object specified by the keys and values:

```{r}
keys <- c("country", "city", "zipcode", "address", "DOB", "occupation", "degree")
values <- c("US", "Indianapolis", "46202", "410 W Tenth St.", "01/01/2017", "Data Scientist", "PhD")

paste(keys, values, sep =": " , collapse=" ")
```

##2) Write three ways to come up with all odd integers between 1 and 35 (including 1 and 35)

```{r}
#first
seq(1, 35, by=2)

#Second
a<-1:35
a[a%%2!=0]

#third
for (i in 1:35){
  if(i%%2!=0){
    print(i)
  }
}

```
## Q3 Using the ChickWeight dataset, provide a histogram of the weight variable using base R graphics.


```{r}
hist(ChickWeight$weight, xlab = 'weights in grams', main ='Histogram of chick weights')

```
Please provide a boxplot of the weight variable by Diet - use the boxplot() function do this.

```{r}
attach(ChickWeight)
boxplot(weight~Diet, xlab ='Diet', ylab='weight', main = 'Boxplot Diet vs Weight')
```
Do you see anything about this data that is worth noting?


