---
title: "Lab-5"
author: "manohar"
date: "October 22, 2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraryCommands, include = FALSE}
library(ggplot2)
library(scales)
library(grid)
library(gridExtra)
library(MASS)
library(ISLR)
library(car)
library(stringr)
library(gdata)
library(tm)
library(wordcloud)
library(ngram)
```

1) Using the Credit.csv data included in the Lab 5 materials on Canvas, read in this dataset to R and call
it Credit. Then, complete the following:

```{r}
Credit<- read.csv('Credit.csv')
str(Credit)
class(Credit)
```
a) Create a new variable in the Credit dataset called studentLow, which is equal to 1 if the individual is a student with a low balance (defined by Balance < 500) and 0 otherwise

```{r}
Credit$studentLow<-ifelse(Credit$Balance<500, 1, 0)
```


b) Create a new variable in the Credit dataset called studentHigh, which is equal to 1 if the individual is a student with a high balance (defined as the opposited of low balance) and 0 otherwise

```{r}
Credit$studentHigh<-ifelse(Credit$Balance>500, 1, 0)
#View(Credit)
```

c) Define another variable called PercentLimit, defined as the individual’s income divided by their credit limit. What unit are incomes listed in? You should adjust for this.

```{r}
Credit$PercentLimit<-(Credit$Income)/Credit$Limit
```


unit of income can be hourly rate. so assuming they work 40 hours a week for 4 weeks. we multiply with 160. 

```{r}
#The income column can be rate per hour 
Credit$PercentLimit<-(Credit$Income*160)/Credit$Limit
#View(Credit)
```
d) How many individuals have incomes that are at most three times bigger than their credit limit?


```{r}
#View(Credit)
a<- Credit[(Credit$Limit * 3)>Credit$Income*160,]
nrow(a)
```
2) Using the ngram R Package - Using the excerpt1.txt file, create a wordcloud(R package wordcloud,
function wordcloud()) that uses 2-grams and 1-grams from excerpt1.txt (on Canvas under Lab 5). A
2-gram is any contiguous sequence of two items from a given text or sentence (excerpt1.txt). You may
create 2-grams from words that end a sentence and start another sentence as well as end a paragraph
and start another paragraph. 1-grams are all words in the excerpt. Make sure to (1) remove punctuation
and (2) remove stopwords such as “the”, “of”, etc. There are tools already built in R to help you with
this, see below.
You will want to check out the ngram R package and the ngram() function within. Notice that the
wordcloud() function can take arguments words and freq - you will want to use these arguments to create
the wordcloud. Several functions of interest for this exercise: concatenate(), preprocess(), ngram(),
get.phrasetable() all from the ngram R package, and tm_map, Corpus(), and VectorSource() from the
tm R package. Make sure to also use the str() (structure) function in order to look under the hood of some
of the objects you create so that you can access information you might need to create the wordcloud.



```{r}
exCon <- file("excerpt1.txt", "r")
linesEx <- list()
i <- 1
while (TRUE)
{
  currLine <- readLines(exCon, n = 1)
  if (length(currLine) > 0)
  {
    currLineWords <- str_split(currLine, " ")[[1]]
    linesEx[[i]] <- currLineWords
  } else {
    break
  }
  i <- i + 1
}
linesEx <- unlist(linesEx)
close(exCon)


```

```{r}
stopWordsEn <- str_replace_all(stopwords(kind = "en"), "[[:punct:]]", "")
## Remove special characters, question marks, etc.
linesEx <- str_replace_all(linesEx, "[[:punct:]]", "")
linesEx <- tolower(linesEx)
linesEx <- linesEx[!(linesEx %in% stopWordsEn)]
linesEx2g <- ngrams(linesEx, n=2)
pal <- brewer.pal(7,"Blues")
wordcloud(linesEx, scale=c(3,.5), min.freq = 5, max.words = 50, colors = pal[-1:-3], random.order = F)
```
```{r message = FALSE, error=FALSE}
ngram2 <- linesEx[linesEx!=""]
ngstr <- paste(ngram2, collapse = " ")
ng<- ngram(ngstr)
df <- data.frame(get.phrasetable(ng))
wordcloud(df$ngrams,df$freq, scale = c(2.2,0.3),max.words=40,random.order = F, colors=pal)
```

3) Scanning a file into R - please download the families.txt file from Canvas under the Lab 5 materials
and write code to extract all families (in a list) with only a male and female parent and no children -
name this list famList. There are multiple examples in the notes that assist you in writing this code.
Please write your code in the same manner as in the notes.
Your final list of families made up of only a father and mother (no children) should be structured exactly as
follows (but may have different names/families/number of families):
famList <- list(family1 = list(Father = "Hector", Mother = "Mary"),
family2 = list(Father = "Devon", Mother = "Sally"))
famList

```{r}
fam<-scan('families.txt', what = 'family')
index<-list()
k<-1
for (i in fam){
  for (j in 1:6){
    if (i==j){
      index[k]<-which(fam==i)
      k=k+1
  }
 }  
}
```

```{r}
faml<-list()
for (i in 1:5){
  a<-index[i]
  b<-index[i+1]
  faml[paste('family',i)] = list(fam[as.numeric(a):as.numeric(b)])
}
```

```{r}
famlist<-list()
for (i in faml){
    if (any(i=='Ch')){
    }else{
      #famlist[paste('famliy', i[1])]<-i
      print(i[2:5])
    }
}
famlist

```





